Background for transient faults in asynchronous circuits

### 2019-10-12 draft_together3.tex
10-12 after restructuring Lemma1 to FT cases

The induction step is to assume that the induction hypothesis is true for a length $k$ prefix $\sigma_k$ of the trace.  We will prove that the induction hypothesis is also true for all $\sigma_{k+1}$ that exist.  First, in the fault-tolerant circuit, for all possible transitions from current state $s_k$, we show that after applying the half circuit mapping there is either no transitions in the original circuit or it is also a transition of the original circuit, and thus P1 is true. 
%(very long, very badly worded sentence, need to fix it)  
Second, we show for all possible next states $s_{k+1}$ that P2 is true and all wire blocks in $s_{k+1}$ are in one of the cases in Figure \ref{fig:l1helper}.\\

Since P1 and P2 are true for all states in $\sigma_k$, they must also be true for the current state $s_k$. From state $s_k$, we examine all possible transitions that change wire values in the A-half; a transition may occur on excited gates or C-elements.  We ignore transitions in the B-half because those transitions do not change wire values in the A-half and the resulting states are deleted during the half circuit mapping.  Wire blocks in the A-half are in one of the cases in Figure \ref{fig:l1helper}, thus transitions in the A-half can only occur in wire blocks that are in cases 1-4 of the figure.  (By P2, if a wire block $w$ 
%(is wire block defined?) 
is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$.  To cover all transitions, it suffices to examine transitions in an excited wire block from cases 1-4.  )

@@

We first show that P1 is true for $\sigma_{k+1}$.  We consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}). %(maybe still need to be more clear about wire block vs transitions) 
If an excited wire block $w$ is in any of these 3 cases, there is only one possible transition for each case: the new value of the signal propagates down the C-element chain.  Thus in the new state $s_{k+1}$, wire block $w$ is in cases 2-4 respectively.  For all 3 cases, the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.  This is a repeated state under the half circuit mapping and is deleted in the resulting trace.  Thus $h^{A}(\sigma_{k+1})=h^{A}(\sigma_k)$ and therefore $h^{A}(\sigma_{k+1})$ must also be a prefix of a trace of the original circuit. \\
Case 4 is when $w^A$ transitions in the fault-tolerant circuit, as shown in case d of Figure \ref{fig:l1helper}.  Then in the original circuit, the transition from state $h^A(s_k)$ to state $h^A(s_{k+1})$ is on wire $w$.  Because wire $w$ is excited in state $h^A(s_k)$, this is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and $h^{A}(\sigma_{k+1})$ is a prefix of a trace of the original circuit. \\

@@

\begin{itemize}
\item Again, we consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}).  We use the following fact from the P1 proof: in the new state $s_{k+1}$, the wireblock $w$ is in cases 2-4 respectively and $h^A(s_{k+1})=h^A(s_{k})$.  Since $h^A(s_{k+1})=h^A(s_{k})$, then all wires in the original circuit do not change excitations in the new state $h^A{s_{k+1}}$.  Then $w$ in the original circuit remains excited in state $h^A{s_{k+1}}$, while wireblock $w$ in the fault tolerant circuit is in one of cases 2-4 in state $s_{k+1}$.  Thus, wireblock $w$ satisfies P2.  All other wireblocks in the fault-tolerant circuit do not change cases in the new state $s_{k+1}$.  %(explain why? does it involve `P2')  
Thus all wireblocks of the fault-tolerant circuit in state $s_{k+1}$ satisfy P2, so P2 is true for the trace $\sigma_{k+1}$.

@@

\item The last case is when a transition occurs from case 4.  That is, $w^A$ transitions in the fault-tolerant circuit from case d of Figure \ref{fig:l1helper}.  %The original circuit transitions to state $h^A(s_{k+1})$ where wire $w$ transitions.
As mentioned in the P1 proof, applying the half circuit mapping results in wire $w$ transitioning in the original circuit.  
%applying the $h^A$ mapping to state $s_{k+1}$ indicates that $w$ transitions in the original circuit.  
We show this transition affects the excitation state of wire blocks/wires in both the fault-tolerant circuit and the original circuit such that P2 is satisfied for $s_{k+1}$.  By P2 of state $s_k$, we partition the wire blocks in the fault-tolerant circuit in state $s_k$ into five cases, as described in Figure \ref{fig:l1helper}.  Note that because wire $w^A$ transitions, wireblock $w$ is a special case of case 4 which we deal with separately from other wireblocks in case 4.
%Next we show P3 holds by examining $w$/$w^A$'s effects in the other wires/wire blocks.  A change in wire $w$ fans out to other logic blocks which may change their excitations in response.  Thus we partition the output wires in the original circuit into four categories: wires that are excited in the current state and excited in the next state, wires that are excited in the current state and unexcited in the next state, wires that are unexcited in the current state and are newly excited in the next state, and wires that are unexcited in the current state and unexcited in the next state.
%these are the only possibilities in the original... look at what happens to these wires in the FT circuit
\begin{itemize}
\item
For wireblocks in cases 1-4 (not including wireblock $w$), we show that these wireblocks remain in the same case in state $s_{k+1}$.  Let us call a wireblock in one of these states as $v$.  By P2 of state $s_k$, wire $v$ of the original circuit is excited in state $h^A(s_{k})$.  Since the original circuit is semi-modular and $v$ does not transition, then $v$ must remain excited in state $h^A(s_{k+1})$.  In the fault tolerant circuit, we only need to examine the logic block portion of the wireblock since the transition is not in $v$.  \\
state $s_{k+1}$ Case 1 is straight forward since the inputs of $c1^A$ in the fault-tolerant circuit and $v$ in the original circuit are equal under the half circuit mapping and the wire values $c1^A$ and $v$ are equal as well.  Therefore $c1^A$ must have the same excitation as $v$, that is, excited.  If $v$ is in case 1 in state $s_k$, then $c1^A$ remains excited in state $s_{k+1}$ with no other transitions in $v$, thus $v$ is in case 1 in state $s_{k+1}$.  \\
In Cases 2-4, the logic block of the fault-tolerant circuit is unexcited while $v$ is still excited in the original circuit.  The logic block of the fault-tolerant circuit remains unexcited in state $s_{k+1}$, which is by contradiction.  Suppose that there is some $v$ where the logic block becomes excited in state $s_{k+1}$, then $v$ in the original circuit and $c1^A$ in the fault tolerant circuit are excited in opposite directions.  Since the logic blocks for $v$ and $c1^A$ are identical and one of gates or C-element, the excitation is determined purely by its inputs.  Again the inputs to $c1^A$ and $v$ are equal so these input values cause the logic block to excite to both 1 and 0 at the same time.  This cannot happen in any of the elements that we build are circuit from and is therefore a contradiction. %(change this into a new lemma?)  
Thus, if $v$ is in case 2-4 in state $s_k$, then $c1^A$ remains unexcited in state $s_{k+1}$ with no other transitions in $v$, thus $v$ is in case 2-4 in state $s_{k+1}$.  
Combined with $v$ staying excited in the original circuit in state $h^A(s_{k+1})$, any wireblocks in these 4 cases satisfy P2 in state $s_{k+1}$.

>>>>

The induction step is to assume that the induction hypothesis is true for a length $k$ prefix $\sigma_k$ of the trace.  We will prove that the induction hypothesis is also true for all $\sigma_{k+1}$ that exist.  First, in the fault-tolerant circuit, for all possible transitions from current state $s_k$, we show that after applying the half circuit mapping there is either no transitions in the original circuit or it is also a transition of the original circuit, and thus P1 is true. (very long, very badly worded sentence, need to fix it)  
Second, we show for all possible next states $s_{k+1}$ that P2 is true and all wire blocks in $s_{k+1}$ are in one of the cases in Figure \ref{fig:l1helper}.\\

Since P1 and P2 are true for all states in $\sigma_k$, they must also be true for the current state $s_k$. From state $s_k$, we examine all possible transitions that change wire values in the A-half; a transition may occur on excited gates or C-elements.  We ignore transitions in the B-half because those transitions do not change wire values in the A-half and the resulting states are deleted during the half circuit mapping.  Wire blocks in the A-half are in one of the cases in Figure \ref{fig:l1helper}, thus transitions in the A-half can only occur in wire blocks that are in cases 1-4 of the figure.  (By P2, if a wire block $w$ 
(is wire block defined?) 
is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$.  To cover all transitions, it suffices to examine transitions in an excited wire block from cases 1-4.  )

@@

We first show that P1 is true for $\sigma_{k+1}$.  We consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}). (maybe still need to be more clear about wire block vs transitions) 
If an excited wire block $w$ is in any of these 3 cases, there is only one possible transition for each case: the new value of the signal propagates down the C-element chain.  Thus in the new state $s_{k+1}$, wire block $w$ is in cases 2-4 respectively.  For all 3 cases, the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.  This is a repeated state under the half circuit mapping and is deleted in the resulting trace.  Thus $h^{A}(\sigma_{k+1})=h^{A}(\sigma_k)$ and therefore $h^{A}(\sigma_{k+1})$ must also be a prefix of a trace of the original circuit. \\
Case 4 is when $w^A$ transitions in the fault-tolerant circuit, as shown in case d of Figure \ref{fig:l1helper}.  Then in the original circuit, the transition from state $h^A(s_k)$ to state $h^A(s_{k+1})$ is on wire $w$.  Because wire $w$ is excited in state $h^A(s_k)$, this is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and $h^{A}(\sigma_{k+1})$ is a prefix of a trace of the original circuit. \\

@@

\begin{itemize}
\item Again, we consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}).  We use the following fact from the P1 proof: in the new state $s_{k+1}$, the wireblock $w$ is in cases 2-4 respectively and $h^A(s_{k+1})=h^A(s_{k})$.  Since $h^A(s_{k+1})=h^A(s_{k})$, then all wires in the original circuit do not change excitations in the new state $h^A{s_{k+1}}$.  Then $w$ in the original circuit remains excited in state $h^A{s_{k+1}}$, while wireblock $w$ in the fault tolerant circuit is in one of cases 2-4 in state $s_{k+1}$.  Thus, wireblock $w$ satisfies P2.  All other wireblocks in the fault-tolerant circuit do not change cases in the new state $s_{k+1}$.  (explain why? does it involve `P2')  
Thus all wireblocks of the fault-tolerant circuit in state $s_{k+1}$ satisfy P2, so P2 is true for the trace $\sigma_{k+1}$.

@@

\item The last case is when a transition occurs from case 4.  That is, $w^A$ transitions in the fault-tolerant circuit from case d of Figure \ref{fig:l1helper}.  %The original circuit transitions to state $h^A(s_{k+1})$ where wire $w$ transitions.
As mentioned in the P1 proof, applying the half circuit mapping results in wire $w$ transitioning in the original circuit.  
%applying the $h^A$ mapping to state $s_{k+1}$ indicates that $w$ transitions in the original circuit.  
We show this transition affects the excitation state of wire blocks/wires in both the fault-tolerant circuit and the original circuit such that P2 is satisfied for $s_{k+1}$.  By P2 of state $s_k$, we partition the wire blocks in the fault-tolerant circuit in state $s_k$ into five cases, as described in Figure \ref{fig:l1helper}.  Note that because wire $w^A$ transitions, wireblock $w$ is a special case of case 4 which we deal with separately from other wireblocks in case 4.
%Next we show P3 holds by examining $w$/$w^A$'s effects in the other wires/wire blocks.  A change in wire $w$ fans out to other logic blocks which may change their excitations in response.  Thus we partition the output wires in the original circuit into four categories: wires that are excited in the current state and excited in the next state, wires that are excited in the current state and unexcited in the next state, wires that are unexcited in the current state and are newly excited in the next state, and wires that are unexcited in the current state and unexcited in the next state.
%these are the only possibilities in the original... look at what happens to these wires in the FT circuit
\begin{itemize}
\item
For wireblocks in cases 1-4 (not including wireblock $w$), we show that these wireblocks remain in the same case in state $s_{k+1}$.  Let us call a wireblock in one of these states as $v$.  By P2 of state $s_k$, wire $v$ of the original circuit is excited in state $h^A(s_{k})$.  Since the original circuit is semi-modular and $v$ does not transition, then $v$ must remain excited in state $h^A(s_{k+1})$.  In the fault tolerant circuit, we only need to examine the logic block portion of the wireblock since the transition is not in $v$.  \\
state $s_{k+1}$ Case 1 is straight forward since the inputs of $c1^A$ in the fault-tolerant circuit and $v$ in the original circuit are equal under the half circuit mapping and the wire values $c1^A$ and $v$ are equal as well.  Therefore $c1^A$ must have the same excitation as $v$, that is, excited.  If $v$ is in case 1 in state $s_k$, then $c1^A$ remains excited in state $s_{k+1}$ with no other transitions in $v$, thus $v$ is in case 1 in state $s_{k+1}$.  \\
In Cases 2-4, the logic block of the fault-tolerant circuit is unexcited while $v$ is still excited in the original circuit.  The logic block of the fault-tolerant circuit remains unexcited in state $s_{k+1}$, which is by contradiction.  Suppose that there is some $v$ where the logic block becomes excited in state $s_{k+1}$, then $v$ in the original circuit and $c1^A$ in the fault tolerant circuit are excited in opposite directions.  Since the logic blocks for $v$ and $c1^A$ are identical and one of gates or C-element, the excitation is determined purely by its inputs.  Again the inputs to $c1^A$ and $v$ are equal so these input values cause the logic block to excite to both 1 and 0 at the same time.  This cannot happen in any of the elements that we build are circuit from and is therefore a contradiction. (change this into a new lemma?)  
Thus, if $v$ is in case 2-4 in state $s_k$, then $c1^A$ remains unexcited in state $s_{k+1}$ with no other transitions in $v$, thus $v$ is in case 2-4 in state $s_{k+1}$.  
Combined with $v$ staying excited in the original circuit in state $h^A(s_{k+1})$, any wireblocks in these 4 cases satisfy P2 in state $s_{k+1}$.
